Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-06 main.Rmd
minor
fixing R citations

```{r hierarchy-cric}

knitr::kable(hierarchy_model,
             format = "latex",
             booktabs = TRUE,
             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
  #row_spec(0, bold = TRUE)%>%
  kable_styling()
```

@@

The authors would like to thank the cohort [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages and Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of smart meter application. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found on the package website [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). This article was created with `knitr` [@knitr, @R-knitr] and `rmarkdown` [@rmarkdown, @R-rmarkdown]. This paper's Github repository, [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.

@@

```{r write-bib, eval = FALSE}
write_bib(c("dplyr", "tidyr", "tsibble", "magrittr", "rlang", "gravitas", "knitr", "rmarkdown"), file = "rpkgs.bib")
```

>>>>

```{r hierarchy-cric}
```

@@

The authors would like to thank the cohort [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages and Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of smart meter application. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found on the package website [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). This article was created with `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown]. This paper's Github repository, [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.

@@

```{r write-bib, eval = FALSE}
write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr"), file = "rpkgs.bib")
```
